Lyman-$\alpha$ photons through rotating outflows

### 2018-03-31 paper/paper.tex
edit

\begin{figure*}
\begin{center}
\includegraphics[height=0.27\textwidth]{./figures/results/line_characterization_std_vout5_logtau5.pdf}
\includegraphics[height=0.27\textwidth]{./figures/results/line_characterization_std_vout25_logtau5.pdf}
\includegraphics[height=0.27\textwidth]{./figures/results/line_characterization_std_vout50_logtau5.pdf}
\includegraphics[height=0.27\textwidth]{./figures/results/line_characterization_std_vout5_logtau6.pdf}
\includegraphics[height=0.27\textwidth]{./figures/results/line_characterization_std_vout25_logtau6.pdf}
\includegraphics[height=0.27\textwidth]{./figures/results/line_characterization_std_vout50_logtau6.pdf}
\includegraphics[height=0.27\textwidth]{./figures/results/line_characterization_std_vout5_logtau7.pdf}
\includegraphics[height=0.27\textwidth]{./figures/results/line_characterization_std_vout25_logtau7.pdf}
\includegraphics[height=0.27\textwidth]{./figures/results/line_characterization_std_vout50_logtau7.pdf}
\end{center}
\caption{\textbf{Standard Deviation trends.} Results for all the
  Radiative Transfer simulations (in triangles) compares against the
  Doppler Shift model (lines).
  All panels correspond to a viewing angle of $\theta = 90^{\circ}$
  (perpendicular to the rotation axis). 
  The optical depth increases from top to bottom and the outflow
  velocity from left to right.
  \label{fig:standard_deviation}}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[height=0.27\textwidth]{./figures/results/line_characterization_skw_vout5_logtau5}
\includegraphics[height=0.27\textwidth]{./figures/results/line_characterization_skw_vout25_logtau5}
\includegraphics[height=0.27\textwidth]{./figures/results/line_characterization_skw_vout50_logtau5}
\includegraphics[height=0.27\textwidth]{./figures/results/line_characterization_skw_vout5_logtau6}
\includegraphics[height=0.27\textwidth]{./figures/results/line_characterization_skw_vout25_logtau6}
\includegraphics[height=0.27\textwidth]{./figures/results/line_characterization_skw_vout50_logtau6}
\includegraphics[height=0.27\textwidth]{./figures/results/line_characterization_skw_vout5_logtau7}
\includegraphics[height=0.27\textwidth]{./figures/results/line_characterization_skw_vout25_logtau7}
\includegraphics[height=0.27\textwidth]{./figures/results/line_characterization_skw_vout50_logtau7}
\end{center}
\caption{\textbf{Skewness trends.} Results for all the
  Radiative Transfer simulations (in triangles) compares against the
  Doppler Shift model (lines).
  Follows the same layout as Figure \ref{fig:standard_deviation}. 
  \label{fig:skewness}}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_bi_vout5_logtau5}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_bi_vout25_logtau5}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_bi_vout50_logtau5}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_bi_vout5_logtau6}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_bi_vout25_logtau6}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_bi_vout50_logtau6}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_bi_vout5_logtau7}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_bi_vout25_logtau7}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_bi_vout50_logtau7}
\end{center}
\caption{\textbf{Bimodality trends.} Results for all the
  Radiative Transfer simulations (in triangles) compares against the
  Doppler Shift model (lines). 
  Follows the same layout as Figure \ref{fig:standard_deviation}. 
  \label{fig:bimodality}}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau5}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau5}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau5}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau6}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau6}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau6}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau7}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau7}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau7}
\end{center}
\caption{\textbf{Valley Intensity:} We show for each \tauh the dependency that
		the viewing angle $\theta$ has on the line's the valley intensity. The larger
		$\cos{\theta}$ the lower is the valley intensity, so the higher $\theta$, the
		higher the valley intensity. Also, the higher \tauh, the better is the fit RT-DS.
		We fixed $\vrot=100$\kms.
		\label{fig:valley_intensity}}
\end{figure*}

\begin{figure}
  \begin{center}
    \includegraphics[width=0.48\textwidth]{./figures/discussion/doppler}
  \end{center}
  \caption{\textbf{Spectra from receeding/approaching sides of a toy
      model LAE.}  These results correspond to the RT simulation with
    $\vout=25$\kms, $\vrot=50$\kms, $\tauh=10^5$. 
    The spectra were computed for a viewing angle of
    $\theta=90^{\circ}$. This toy model illustrates to what extent spectra from
    opposite sides of a galaxy have an imprint of the rotational
    kinematics. 
    \label{fig:doppler}}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=0.48\textwidth]{./figures/results/muse_vs_simulations.pdf}
  \end{center}
  \caption{\textbf{Comparison between simulations and observations.}  
    \label{fig:muse}}
\end{figure}

@@

Another application of this new model to the current interpretation of \lya
spectra, is that the central ($V=0$) emission of the spectra seen in the
\lya line, is a consequence of the viewing angle of the galaxy and can be
controlled by it. 
Several authors have suggested that this central emission is caused by
radiation that escapes the galaxy without scattering. 
Rotation is an alternative that solves this issue.

@@

@@

Current observational facilities have the capability of spatially
resolving the extent of a LAE.
For instance \cite{Prescott14} presented observational results of a
Doppler shift when taking spectra at two oposite sides of a large
($\approx 80$kpc) LAE.

@@

Addressing the second question we posed in the introduction (To what
extent is possible to constrain rotational kinematics from the \lya
emission line?)  we can say that as an application to observational data our results suggest that
rotation should also be considered as an explanation of the
non-vanishing \lya intensity at the line's center.

A more straightfoward approach is takes into account how the
\lya spectra from two different sides of a galaxy can detect
approaching/receeding gas motions.
In that case one has to be careful and take into account that the
peaks of these two spectra is smaller than the expected value of
$2\times\vrot$ due to the differente weights at the surface of the
emitting regions.

>>>>

\begin{figure*}
\begin{center}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_std_vout5_logtau5.pdf}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_std_vout25_logtau5.pdf}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_std_vout50_logtau5.pdf}\\
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_std_vout5_logtau6.pdf}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_std_vout25_logtau6.pdf}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_std_vout50_logtau6.pdf}\\
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_std_vout5_logtau7.pdf}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_std_vout25_logtau7.pdf}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_std_vout50_logtau7.pdf}
\end{center}
\caption{\textbf{Standard Deviation trends.} Results for all the
  Radiative Transfer simulations (in triangles) compares against the
  Doppler Shift model (lines).
  All panels correspond to a viewing angle of $\theta = 90^{\circ}$
  (perpendicular to the rotation axis). 
  The optical depth increases from top to bottom and the outflow
  velocity from left to right.
  \label{fig:standard_deviation}}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_skw_vout5_logtau5}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_skw_vout25_logtau5}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_skw_vout50_logtau5}\\
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_skw_vout5_logtau6}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_skw_vout25_logtau6}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_skw_vout50_logtau6}\\
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_skw_vout5_logtau7}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_skw_vout25_logtau7}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_skw_vout50_logtau7}
\end{center}
\caption{\textbf{Skewness trends.} Results for all the
  Radiative Transfer simulations (in triangles) compares against the
  Doppler Shift model (lines).
  Follows the same layout as Figure \ref{fig:standard_deviation}. 
  \label{fig:skewness}}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_bi_vout5_logtau5}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_bi_vout25_logtau5}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_bi_vout50_logtau5}\\
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_bi_vout5_logtau6}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_bi_vout25_logtau6}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_bi_vout50_logtau6}\\
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_bi_vout5_logtau7}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_bi_vout25_logtau7}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_bi_vout50_logtau7}
\end{center}
\caption{\textbf{Bimodality trends.} Results for all the
  Radiative Transfer simulations (in triangles) compares against the
  Doppler Shift model (lines). 
  Follows the same layout as Figure \ref{fig:standard_deviation}. 
  \label{fig:bimodality}}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau5}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau5}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau5}\\
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau6}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau6}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau6}\\
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau7}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau7}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau7}
\end{center}
\caption{\textbf{Valley Intensity:} We show for each \tauh the dependency that
		the viewing angle $\theta$ has on the line's the valley intensity. The larger
		$\cos{\theta}$ the lower is the valley intensity, so the higher $\theta$, the
		higher the valley intensity. Also, the higher \tauh, the better is the fit RT-DS.
		We fixed $\vrot=100$\kms.
		\label{fig:valley_intensity}}
\end{figure*}

\begin{figure}
\centering
    \includegraphics[width=0.48\textwidth]{./figures/discussion/doppler}
  \caption{\textbf{Spectra from receeding/approaching sides of a toy
      model LAE.}  These results correspond to the RT simulation with
    $\vout=25$\kms, $\vrot=50$\kms, $\tauh=10^5$. 
    The spectra were computed for a viewing angle of
    $\theta=90^{\circ}$. This toy model illustrates to what extent spectra from
    opposite sides of a galaxy have an imprint of the rotational
    kinematics. 
    \label{fig:doppler}}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.48\textwidth]{./figures/results/muse_vs_simulations.pdf}

\caption{\textbf{Comparison between simulations and observations.}  
  \label{fig:muse}}
\end{figure}

@@

Another application of this new model to the current interpretation of \lya
spectra, is that the central ($V=0$) emission of the spectra seen in the
\lya line, is a consequence of the viewing angle of the galaxy and can be
controlled by it. 
Several authors have suggested that this central emission is caused by
radiation that escapes the galaxy without scattering, mostly due to a
clumpy interstellear medium \citep{Hansen06, 2016ApJ...833L..26G}.
Rotation is an alternative that solves this issue.

@@

A recent observational example is provided by
\cite{2017A&A...608L...4R}.
They report optical spectroscopy of a bright lensed galaxy at a
redshift of $z=2.4$. 
The object presents a triple peaked \lya profile that can be thought
as the superposition of two components, a double asymmetric peak and a
narrower symmetric peak around the line's center.
One possible option for the narrow component is that it escaped the
galaxy without substantial interaction with neutral Hydrogen.
We especulate that the central feature could also be due to a purely 
rotating compont that can produce such a feature as shown by
\cite{tololo}. The triple peak could be then produced by two main
decopled components one rotating the other outflowing.

Another interesting example are the \lya lines in Green Pea galaxies \citep{2016ApJ...820..130Y}.
\cite{2017ApJ...844..171Y} showed in a study of 43 Green Pea galaxies
that 2/3 were strong \lya emitters. 
Because the \lya escape fraction is estimated from the ration of
H$\alpha$ to \lya at the respective line's center, the authors infer
large escape fractions for galaxies with substantial \lya emission at
the lines'center.
We especulate that these features could also be the product of
rotation in those galaxies.

@@

Current observational facilities have the capability of spatially
resolving the extent of a LAE.
For instance \cite{Prescott14} presented observational results of a
Doppler shift when taking spectra at two oposite sides of a large
($\approx 80$kpc) LAE.
In more recent work \cite{2018MNRAS.473.3907A} mapped \lya emission
around a quasar

@@

Addressing the second question we posed in the introduction (To what
extent is possible to constrain rotational kinematics from the \lya
emission line?)  we can say that as an application to observational data our results suggest that
rotation should also be considered as an explanation of the
non-vanishing \lya intensity at the line's center, which could change
the interpretation of recent observational results
\citep[e.g.][]{2017ApJ...844..171Y,2017A&A...608L...4R} that claim
instead that this flux constrains the escape fraction of \lya
radiation.

A more straightfoward approach takes into account how the
\lya spectra from two different sides of a galaxy can detect
approaching/receeding gas motions.
In that case one has to be careful and take into account that the
peaks of these two spectra is smaller than the expected value of
$2\times\vrot$ due to the differente weights at the surface of the
emitting regions.
